Java Based Memory Latency Simulator

### 2020-11-21 finalPaper/paper.tex
Update paper.tex

Not all of this information, especially concerning network is that closely relevant to our field of study, but
we can certianly see the latencies that included reading, writing and referencing from the CPU caches, memory
and the drives had a huge difference in between them. The low level operations that took place within the
CPU were the quickest of all, referencing Caches and branching. Secondly referencing the RAM (7 ns) was slower than
referencing the the caches (0.5 ns and 7 ns) but alot faster that going to a and reading from disk which was almost a
20 million times slower than refernecing the L1 Cache and upto a hundred thousand times slower than referencing
the RAM.

@@

The goal of the project was to find out about the varying latencies of some of the major components of the CPU, with
or without the simulator. By implementing a simulator good enough to differentiate and manage data we were able to
find out more about the memory management in an environment ran by threads. However, since there exists some complex
and deep details and components in the real world units that we represented, we were only able to implement as much
as the basic level of each component.
The real world data that we represented made up most of our information in the paper, but that was along with the
fact that the data we imported, was a combination of several different projects and researchs.
Starting from the hard drive we did not represent the sectors, platters and other mechanical components, instead
we implemented the HDD using data blocks, thus we were only able to gather stats for a sequential read and write.
A similar implementation of RAM meant that we did not explicitly render the memory cells in the RAM but only the
data blocks which act as those cells.
For the CPU we only represented a single level of cache a L1, while almost all the modern CPUS work on dual level
of cache.
Being programmed in java our simulator was bounded by the high level barrier, so to represent the low
level of memory management, we did have to implement delays ourselves. Our delays were then rationalized according
to the time it takes in the low level. 
A lot that was not gathered through the simulator, a deep analysis of sources did cover for that. Especially getting
to know the latencies of new combinations of components that we did not implement in out simulator helped us to a
more realistic approach. The research itself was based upon a latency simulator with a concentration on what makes
up the delays in a real world programming system.

@@

Memory Management within a memory system is a complex set of organizations of several different peices, which
themselves are a set of several different elements. So if we are to study the time delays as a superset of
memory latencies, we cannot just discuss the general latencies of each component seperately. But one must
realize that the components are very closely linked with each other. An example of this would be that if a
a CPU references either  cache and it hits, that would be an ideal situation for the a real model, but if does
not find what it needs then it has to ref the memory or eventually the Disks, resulting in so many differnt
factors for delays, including but not only, the CAS latency of the RAM, the HDD I/O latency, which further
includes the delays of rotation, read write head, settling time etc.

>>>>

Not all of this information, especially concerning network is that closely relevant to our field of study, but
we can certianly see the latencies that included reading, writing and referencing from the CPU caches, memory
and the drives had a huge difference in between them. The low level operations that took place within the
CPU were the quickest of all, referencing Caches and branching. Secondly referencing the RAM (7 ns) was slower than
referencing the the caches (0.5 ns and 7 ns) but alot faster that going to a and reading from disk which was almost a
20 million times slower than referencing the L1 Cache and upto a hundred thousand times slower than referencing
the RAM.

@@

The goal of the project was to find out about the varying latencies of some of the major components of the CPU, with
or without the simulator. By implementing a simulator good enough to differentiate and manage data we were able to
find out more about the memory management in an environment ran by threads. However, since there exists some complex
and deep details and components in the real world units that we represented, we were only able to implement as much
as the basic level of each component.
The real world data that we represented made up most of our information in the paper, but that was along with the
fact that the data we imported, was a combination of research and several different projects.
Starting from the hard drive we did not represent the sectors, platters and other mechanical components, instead
we implemented the HDD using data blocks, thus we were only able to gather stats for a sequential read and write.
A similar implementation of RAM meant that we did not explicitly render the memory cells in the RAM but only the
data blocks which act as those cells.
For the CPU we only represented a single level of cache a L1, while almost all the modern CPUs work on dual level
of cache.
Being programmed in java our simulator was bounded by the high level barrier, so to represent the low
level of memory management, we did have to implement delays ourselves. Our delays were then rationalized according
to the time it takes in the low level. 
A lot that was not gathered through the simulator, a deep analysis of sources did cover for that. Especially getting
to know the latencies of new combinations of components that we did not implement in out simulator helped us to a
more realistic approach. The research itself was based upon a latency simulator with a concentration on what makes
up the delays in a real world programming system.

@@

Memory Management within a memory system is a complex set of organizations of several different pieces, which
themselves are a set of several different elements. So if we are to study the time delays as a superset of
memory latencies, we cannot just discuss the general latencies of each component separately. But one must
realize that the components are very closely linked with each other. An example of this would be that if a
a CPU references either  cache and it hits, that would be an ideal situation for the a real model, but if does
not find what it needs then it has to ref the memory or eventually the Disks, resulting in so many different
factors for delays, including but not only, the CAS latency of the RAM, the HDD I/O latency, which further
includes the delays of rotation, read write head, settling time etc.
